A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
added more details on CN2 description.

    \item<1-> Inductive Logic Programming: using Aleph

@@

\frame
{
  \frametitle{Conducted Experiments}
  % colocar ILP CN2 ID3!
}

@@

\subsection{Rule Induction}
\frame
{
    \frametitle{Rule Induction}

    \begin{itemize}
    \item<1-> Peter Clark's CN2 software was used to induce rules:
    \begin{itemize}
        \item<1-> \url{http://www.cs.utexas.edu/users/pclark/software/\#cn2}.
    \end{itemize}
    \item<1-> CN2 can generate both ordered and unordered set of rules.
    \item<1-> Peter Clark's software can use different error estimations:
    \begin{itemize}
        \item<1-> Laplacian.
        \item<1-> Naive.
        \item<1-> Information Gain.
        \item<1-> Modified Entropy.
    \end{itemize}
    \end{itemize}
}

>>>>

    \item<1-> Inductive Logic Programming
    \begin{itemize}
        \item<1-> Aleph
    \end{itemize}

@@

\frame
{
  \frametitle{Conducted Experiments}

  \begin{itemize}
    \item<1-> RapidMiner was used to build a classifier with the ID3 algorithm.
    \item<1-> Peter Clark's CN2 was used to induce rules.
    \begin{itemize}
        \item<1-> \url{http://www.cs.utexas.edu/users/pclark/software/\#cn2}.
    \end{itemize}
    \item<1-> Aleph was used to inductively generate logic clauses.
    \begin{itemize}
        \item<1-> \url{http://www.comlab.ox.ac.uk/activities/machinelearning/Aleph/aleph.html}.
    \end{itemize}
  \end{itemize}
  % colocar ILP ID3!
}

@@

\subsection{CN2}
\frame
{
    \frametitle{CN2}

    \begin{itemize}
    \item<1-> CN2 can generate both ordered and unordered set of rules.
    \item<1-> Peter Clark's software can use different error estimations:
    \begin{itemize}
        \item<1-> Laplacian.
        \item<1-> Naive.
        \item<1-> Information Gain.
        \item<1-> Modified Entropy.
    \end{itemize}
    \end{itemize}

\footnotesize
\begin{table}[ht]
\begin{center}
\begin{tabular}{ | l | l | l | l | l |}
    \hline
    \textbf{Algorithm} & \textbf{Error estimate} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    Unordered & Laplacian & 13.3 & 15.2 & 3m29s \\ \hline
    Unordered & Naive & - & - & - \\ \hline
    Ordered & Laplacian & 0 & 17.6 & 1m45s \\ \hline
    Ordered & Naive & 0 & 19.9 & 12m21s \\ \hline
    Ordered & Information Gain & 18.9 & 18.9 & 0m5s \\ \hline
    Ordered & Modified Entropy & 18.9 & 19.1 & 0m20s \\ \hline
\end{tabular}
\end{center}
\end{table}
\normalsize
}
